Local-to-Global Mariculture Modelling

### 2025-12-16 docs-working/05_formulating_feeds.qmd
Updates

library(arrow)
library(sf)
library(dplyr)
library(tidyr)
library(terra)
library(magrittr)
library(purrr)
library(furrr)
library(future)
library(tictoc)
library(ggplot2)
library(fs)
library(conflicted)
library(stringr)
library(readxl)
library(units)
library(qs)
library(here)
conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)

>>>>

library(tidyverse)
library(arrow)
library(sf)
library(terra)
library(furrr)
library(future)
library(tictoc)
library(fs)
library(conflicted)
library(readxl)
library(units)
library(qs)
library(here)
conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)

### 2025-12-16 docs-working/08_data_analysis.qmd
Updates

The purpose of this script is to take the raw model outputs and save them as files which answer (or go towards answering) specific questions. These files can then be directly called by index.qmd to quickly create plots or text summaries.

```{r}
#| label: setup
#| warning: false
#| message: false

library(arrow)
library(sf)
library(dplyr)
library(tidyr)
library(terra)
library(magrittr)
library(purrr)
library(furrr)
library(future)
library(tictoc)
library(ggplot2)
library(fs)
library(conflicted)
library(stringr)
library(readxl)
library(units)
library(qs)
library(here)
library(targets)
conflicted::conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)

@@

>>>>

This script takes outputs from the targets pipeline.

```{r setup}
#| warning: false
#| message: false

library(tidyverse)
library(arrow)
library(sf)
library(terra)
library(magrittr)
library(furrr)
library(future)
library(tictoc)
library(fs)
library(conflicted)
library(readxl)
library(units)
library(qs)
library(here)
library(targets)
conflicted::conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)

@@

```{r filenames}
#| code-summary: Set up global filenames

# Filenames
# species_params_excel <- c(file = file.path(input_species_param_path, "Species.xlsx"), sheet = "Atlantic salmon")
# pop_params_excel <- c(file = file.path(input_species_param_path, "Population.xlsx"))
# farm_locations_parquet <- file.path(input_farm_coords_path, "farm_coords.parquet")
# farm_coords_file <- file.path(output_farm_data_path, "farm_coords.qs")
# farm_geometry_file <- file.path(output_farm_data_path, "farm_geometry.qs")
# farm_ts_data_file <- file.path(output_farm_data_path, "farm_ts_data.qs")
# species_params_file <- file.path(output_species_data_path, "species_params.qs")
# sens_params_file <- file.path(output_species_data_path, "sens_params.qs")
# pop_params_file <- file.path(output_species_data_path, "pop_params.qs")
# feed_params_file <- file.path(output_species_data_path, "feed_params.qs")
# farm_harvest_file <- file.path(output_farm_data_path, "farm_harvest_size.qs")
```

# Look at raw outputs

```{r raw-outputs}
total_ends <- qread(file.path(output_model_farm_path, "total_ends.qs")) %>% 
  mutate(
    feed_group = as.factor(str_remove(feed, "_min|_max")),
    feed_type = case_when(
      str_detect(feed, "_min") ~ "min",
      str_detect(feed, "_max") ~ "max",
      T ~ "mean"
    ) %>% as.factor(),
    mean = set_units(mean, "g"),
    sd = set_units(sd, "g"),
    mean_biomass = set_units(mean, "g g_fish-1"),
    sd_biomass = set_units(sd, "g g_fish-1")
  )

cohort_results <- qread(file.path(output_model_cohort_path, "cohort_results.qs")) %>% 
  mutate(
    feed_group = as.factor(str_remove(feed, "_min|_max")),
    feed_type = case_when(
      str_detect(feed, "_min") ~ "min",
      str_detect(feed, "_max") ~ "max",
      T ~ "mean"
    ) %>% as.factor()
  )
```

# Feed provided and lost

```{r feed-prov-lost}
#| code-summary: Show differences between diets in feed provided and lost
#| fig-cap: Mean food provided and uneaten feed lost to the environment (g/g salmon)

feed_end <- total_ends %>% 
  filter(measure %in% c("total_uneat_stat", "food_prov_stat")) %>% 
  mutate(measure = droplevels(measure))

ggplot(
    feed_end, 
    aes(x = feed_group, y = mean_per_biom, fill = feed_type, group = feed)
  ) +
  geom_boxplot() +
  facet_wrap(facets = vars(measure), scales = "free") +
  prettyplot_300()
```

# Faeces excreted

```{r feed-prov-lost}
#| code-summary: Show differences between diets in feed provided and lost

feed_end <- total_ends %>% 
  filter(measure %in% c("total_uneat_stat", "food_prov_stat")) %>% 
  mutate(measure = droplevels(measure))

ggplot(
    feed_end, 
    aes(x = feed_group, y = mean_per_biom, fill = feed_type, group = feed)
  ) +
  geom_boxplot() +
  facet_wrap(facets = vars(measure), scales = "free") +
  prettyplot_300()
```

# Total waste

### 2025-12-16 docs-working/index.qmd
Updates

| Page | Description |
|---------|:-------------------------------------------------|
| **[Data Tidying](01_tidying_data.html)** | Initial data tidying and preparation |
| **[Extracting Production Locations](02_extracting_production_locations.html)** | Identification and processing of mariculture production site locations |
| **[Assessing Species Potential](03_assessing_species_potential.html)** | Evaluation of species suitability for different locations |
| **[Extracting Temperatures](04_extracting_temperatures.html)** | SST data extraction and processing for model inputs |
| **[Formulating Feeds](05_formulating_feeds.html)** | Feed composition formulation for model runs |
| **[Running Atlantic Salmon Model](06_run_atlantic_salmon_model.html)** | Atlantic salmon growth model execution |

## Extra scripts

The extra scripts for this project involved some exploration into potential impacts of nutrient losses. These will likely not make it into the final manuscript.

| Page | Description |
|---------|:-------------------------------------------------|
| **[Species Layers](07_species_layers.html)** | Spatial analysis of species distribution layers, to try and acertain impacts on vulnerable species |
| **[Relative N Inputs](08_relative_N_inputs.html)** | Analysis of nitrogen input (runoff) patterns and the relative impacts of farm nutrients |

>>>>

| Page | Description |
|---------|:-------------------------------------------------|
| **[Data Tidying](01_tidying_data.html)** | Initial data tidying and preparation |
| **[Extracting Production Locations](02_extracting_production_locations.html)** | Identification and processing of mariculture production site locations |
| **[Assessing Species Potential](03_assessing_species_potential.html)** | Evaluation of species suitability for different locations |
| **[Extracting Temperatures](04_extracting_temperatures.html)** | SST data extraction and processing for model inputs |
| **[Formulating Feeds](05_formulating_feeds.html)** | Feed composition formulation for model runs |
| **[How many runs per farm?](06_how_man_runs_per_farm.html)** | Determining how many Monte-Carlo runs is enough |
| **[Running Atlantic Salmon Model](06_run_atlantic_salmon_model.html)** | Atlantic salmon growth model execution |
| **[Data Analysis](08_data_analysis.html)** | Analysing the outputs of the Atlantic salmon growth model |
| **[Figures for manuscript](09_figures_for_manuscript.html)** | Code used to generate the specific figures used in the manuscript |
